Poisson approximate likelihood compared to the particle filter

### 2024-09-04 ms.Rnw
minor correction

<<OvOv-model, echo=F, warning=F, message=F>>=
# measurement model 
dmeas <- Csnippet("
  lik =  dbinom(cases1, H1, q1, 1) +
  dbinom(cases2, H2, q2, 1) +
  dbinom(cases3, H3, q3, 1);"
)
rmeas <-  Csnippet("
  cases1 = rbinom(H1, q1);
  cases2 = rbinom(H2, q2);
  cases3 = rbinom(H3, q3);
")

@@

sir_sbh_init <- pomp(
  sir_wwr,
  data = dat_sbh,
  times = "time",
  t0 = 1-6*52,
  rinit = rinit_stocks,
  statenames = statenames
)

>>>>

<<OvOv-model, echo=F, warning=F, message=F>>=
# measurement model 
dmeas <- Csnippet("
  if(ISNA(cases1)) {
    lik = (give_log) ? 0 : 1;
  } else {
      lik =  dbinom(cases1, H1, q1, 1) +
      dbinom(cases2, H2, q2, 1) +
      dbinom(cases3, H3, q3, 1);
    }
  lik = (give_log) ? lik : exp(lik);"
)

rmeas <-  Csnippet("
  cases1 = rbinom(H1, q1);
  cases2 = rbinom(H2, q2);
  cases3 = rbinom(H3, q3);
")

@@

sir_sbh_init <- pomp(
  data = dat_sbh,
  times = "time",
  t0 = 1-6*52,
  dmeasure = dmeas,
  rmeasure = rmeas,
  rprocess = discrete_time(step.fun = rproc, delta.t = 1/4),
  statenames = statenames,
  paramnames = names(params_wwr),
  accumvars = c("H1", "H2", "H3"),
  rinit = rinit_stocks,
  partrans = pt_wwr,
  params = params_wwr
)
